TIMES Ireland Model: Residential Sector

### 2021-05-27 manuscript.tex
Done for 27May2021

\subsubsection{TIMES}
\label{Intro:TIMES}

\begin{equation} 
\begin{split}
NPV = {\sum_{r=1}^{R}  \sum_{y\in YEARS}(1 + d_{r,y})^{REFYR-y}}
\cdot {ANNCOST(r,y)} 
\end{split}
%\[ \sum_{n=1}^{\infty} 2^{-n} = 1 \]
\label{Eq:ObjectiveFunction}
\end{equation}
where: $NPV$ is the net present value of the total cost for all regions (the TIMES objective function);
$ANNCOST(r,y)$ is the total annual cost in region r and year y; $d_{r,y}$ is the general discount rate;
$REFYR$ is the reference year for discounting;
YEARS is the set of years for which there are costs, including all years in the horizon, plus past years (before the initial period) if costs have been defined for past investments, plus a number of years after end of the horizon EOH where some investment and dismantling costs are still being incurred, as well as the Salvage Value; and
R is the set of regions in the area of study.
$ANNCOST$ is quite complex and is postponed until section 6.2 of PART II
Due to the data driven nature of TIMES (see section 2.5), all TIMES constraints are activated and defined by specifying some attributes. Attributes are attached to processes, to commodities, to flows, or to special variables that have been created to define new TIMES features. Indeed, TIMES

@@

\subsection{Residential}
\label{LitR:RES}
\subsubsection{Demands}
\label{LitR:Demands }
Macroeconomic 
 The BER database, which represents half of the dwelling stock, highlights the affect year of construction has on expected energy consumption, as shown in Fig.\ref{fig:BERAge}. The BERs labels are categorised based on expected energy consumption, with A1 representing the lowest expected energy consumption ($\leq 74 kWh/m^2/year$) and G representing the highest expected energy consumption ($ >450 kWh/m^2/year$). The BERs are developed from the Energy Performance of Buildings Directive 2002/91/ EC, which helps to better understand the housing stock. BERs are required for new houses, rented houses, sold houses and renovated houses.

@@

\subsubsection{Costs}
\subsubsection{Savings}

>>>>

\subsubsection{TIMES}
\label{Intro:TIMES}
The objective function may be thought of as the discounted sum of net annual costs (i.e. costs minus revenues),
\begin{equation} 
\begin{split}
NPV = {\sum_{r=1}^{R}  \sum_{y\in YEARS}(1 + d_{r,y})^{REFYR-y}}
\cdot {ANNCOST(r,y)} 
\end{split}
%\[ \sum_{n=1}^{\infty} 2^{-n} = 1 \]
\label{Eq:ObjectiveFunction}
\end{equation}
where: $NPV$ is the net present value of the total cost for all regions (the TIMES objective function);
$ANNCOST(r,y)$ is the total annual cost in region r and year y; $d_{r,y}$ is the general discount rate;
$REFYR$ is the reference year for discounting;
YEARS is the set of years for which there are costs, including all years in the horizon, plus past years (before the initial period) if costs have been defined for past investments, plus a number of years after end of the horizon EOH where some investment and dismantling costs are still being incurred, as well as the Salvage Value; and
R is the set of regions in the area of study.
$ANNCOST$ is quite complex and is postponed until section 6.2 of PART II
Due to the data driven nature of TIMES (see section 2.5), all TIMES constraints are activated and defined by specifying some attributes. Attributes are attached to processes, to commodities, to flows, or to special variables that have been created to define new TIMES features. Indeed, TIMES

@@

\subsection{Residential}
\label{LitR:RES}

 The BER database, which represents half of the dwelling stock, highlights the affect year of construction has on expected energy consumption, as shown in Fig.\ref{fig:BERAge}. The BERs labels are categorised based on expected energy consumption, with A1 representing the lowest expected energy consumption ($\leq 74 kWh/m^2/year$) and G representing the highest expected energy consumption ($ >450 kWh/m^2/year$). The BERs are developed from the Energy Performance of Buildings Directive 2002/91/ EC, which helps to better understand the housing stock. BERs are required for new houses, rented houses, sold houses and renovated houses.

@@

\subsubsection{Costs}
\label{LitR:Costs}
\subsubsection{Savings}
\label{LitR:Savings}
\subsubsection{Demands}
\label{LitR:Demands}
Macroeconomic 
Check main TIM paper 
Historical population estimates and future projections are obtained from the Central Statistics Office (CSO), Ireland \citep{CentralStatisticsOffice2020}. We use the M2F1 scenario since it represents medium growth in population and is in line with population projections used in other national sources \citep{Yakut2020}.

\begin{table}[htbp]
\footnotesize
 \centering
 \caption{Energy service demands in TIM}

 \begin{tabular}{p{18em}lccc}
 \hline
    \multirow{Energy Service Demand} & \multirow{Driver} & \multicolumn{2}{c}{Value} & \multirow{Unit} \\
          &       & \multicolumn{1}{c}{2018} & \multicolumn{1}{c}{2050} &  \\ \hline
    Residential Apartment Demand & Population & 206.80 & 628.93 & 000' \\
    Residential Attached Demand & Population & 766.35 & 1056.50 & 000' \\
    Residential Detached Demand & Population & 724.43 & 889.76 & 000' \\
    \hline
    \end{tabular}%

  \label{tab:ESD_list}%
\end{table}%

% Table generated by Excel2LaTeX from sheet 'Population'
\begin{table}[htbp]
 \centering
 \footnotesize
 \caption{Population}
 \begin{tabular}{cc}
 \hline
 Year & Population (millions) \\
 \hline
 2018 & 4.85 \\
 2020 & 4.98 \\
 2030 & 5.40 \\
 2040 & 5.82 \\
 2050 & 6.19 \\
 \hline
 \end{tabular}%
 \label{tab:pop}%
\end{table}%

The residential stock projections upto 2040 are taken from ESRI's housing demand estimates \citep{Bergin2020}. The stock is expected to increase by 40\% from 2018 level with a CAGR of 2\%. This results in an average of 27,600 new houses per annum between between 2021-2040. Beyond 2040, population is used as a driver to project housing stock. The total housing stock obtained in 2050 is 2.57 million which implies 8\% increase from 2040. 
% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
  \centering
  \footnotesize
  \caption{Number of dwellings by type ('000)}
    \begin{tabular}{rrrr}
    \hline
    \multicolumn{1}{l}{Year} & \multicolumn{1}{l}{Apartment} & \multicolumn{1}{l}{Attached } & \multicolumn{1}{l}{Detached} \\ \hline
    2018  & 207   & 766   & 724 \\
    2030  & 355   & 918   & 833 \\
    2040  & 493   & 1003  & 878 \\
    2050  & 629   & 1057  & 890 \\ \hline
    \end{tabular}%
  \label{tab:addlabel}%
\end{table}%
